Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-10-24 DryDep.tex
Finished describtion of dry deposition. Updated plot and added two more for supplement.

The aerodynamic resistance in \citet{WASP:Simpson2003,ACP:Simpson2012} is described as

@@

Over land we use \citep[Eq.~(53),][]{ACP:Simpson2012}

@@

Over ocean we use \citep[Eq.~(54),][]{ACP:Simpson2012}

@@

For the temperature dependent dynamic viscosity of air $\mu(T)$, we chose a linear fit to Southerland's law through the origin within the temperature range $\{T \in \mathbb{R} | (243.15 < T < 313.15)\,\unit{K}\}$: $\mu(T) = 6.2\cdot 10^{-8}\,\unit{kg \, m^{-1} s^{-1} K^{-1}} \cdot T$. But despite its rough acuracy, we found that the choice of $\mu(T)$ has no effect on $\left<R_b\right>$. In Eq.~(\ref{eq:kinematic_viscosity}), $\rho$ is substituted by the air density using the ideal gas law. $P_0$ is the surface pressure, as $T$ the 2\,\unit{m} temperature is chosen, and $R_\text{air}$ is the universal gas constant for air.

@@

  G_c^i = \text{LAI} \cdot G_\text{sto}^i + G_\text{ns}^i, 

@@

wherein $\text{LAI}$ is the leaf area index (zero for non-vegetated surfaces), $G_\text{sto}^i$ the stomatal conductance, and $G_\text{ns}^i$ the non-stomatal conductance.

@@

The stomatal conductance is a measure of the rate of \chem{CO_2} entering or evapotranspiration through the stomata of a leaf. There are several environmental conditions affecting the opening and closing of the stomata and hence their capability of respirationn (e.g., light, available water, etc.). Stomata sluggishness, a state in which the stomata can no longer fully close, has been reported as ozone induced damage \citep{SR:Hoshika2015}. To reflect part of the underlying mechanism, the stomatal conductance $g_\text{STO}$ in the EMAP scheme is computed using a multiplicative ansatz that is also explained in much detail in \citet{ICP:MappingManual2017}:

@@

@@

with $\beta = \frac{T_\text{max}-T_\text{opt}}{T_\text{opt}-T_\text{min}}$. The parameters $T_\text{min}$, $T_\text{max}$ and $T_\text{opt}$ are tabulated for various landsurface types and can be found in the supplementary to \citet{ACP:Simpson2012} or in Supplement~S.2. Since $f_\text{T}$ becomes negative outside its range defined by $T_\text{min}$, $T_\text{max}$, we impose a lower limit of $0.01$. The water vapor deficite (VPD) is proportional to the satuation partial pressure of water ($P_\chem{H_2O}^s$) and relative humidity ($\text{RH}$)

@@

Using tabulated values of $f_\text{min}$, $D_\text{min}$, $D_\text{max}$ (Supplement \citet{ACP:Simpson2012} or Supplement~S.2), the water vapor pressure deficit penalty factor can be computed:

@@

The penalty factor with respect to available water in soil $\text{SW}$ is defined as 

@@

    1 & \quad \text{SW} \geq 0.5,\\
    2 \cdot \text{SW}  & \quad \text{SW} < 0.5.

@@

\citet{ACP:Simpson2012} suggest using SW in soil depths below 1\,\unit{m} (SWVL4 in OpenIFS). Throughout most of our simulations (Section~\ref{sec:eval}), we have instead used the soil water contained in the top layer (SWVL1, $0-7\,\unit{cm}$), which makes the canopy conductance much more sensitive to precipitation than it would be otherwise. The phenology of a plant typically describes its lifecycle though out a year, e.g., in mid latitudes and for decideous species, it starts with the emergence of leafs in spring and ends in fall. In the EMEP scheme phenology is parametrized with respect to the begin of the greening season (GDAY) and its length (GLEN). Details about our choice of GDAY and GLEN are given in Section~\ref{subsubsec:greening}. In summary, the $f_\text{phen}$ parameterization reads as follows:

@@

    \text{GDAY = 0}  & \quad 0 \\
    \text{(GLEN $\ge$ 365} & \quad 1 \quad \emph{explicitly excluding Tropics}) \\

@@

      \text{GDAY} \le \phi_\text{AS}  & \quad \phi_a \\
      \text{GDAY} \le \phi_\text{AS} + \phi_e  & \quad \phi_b+(\phi_c-\phi_b)\cdot(\text{GDAY}-\phi_\text{AS})/\phi_e\\
      \text{GDAY} \le \text{GLEN} - \phi_\text{AE} - \phi_f  & \quad \phi_c\\
      \text{GDAY} \le \text{GLEN} - \phi_\text{AE}  & \quad \phi_d+(\phi_c-\phi_d)\cdot(\text{GLEN}-\phi_\text{AE}-\text{GDAY})/\phi_f\\

@@

The parameters $\phi_a$, $\phi_b$, $\phi_c$, $\phi_d$, $\phi_e$, $\phi_f$, $\phi_\text{AS}$, and $\phi_\text{AE}$ can as well be found in Supplement \citet{ACP:Simpson2012} or Supplement~S.2. If GDAY is zero we are most likely in Arctic regions and there is no vegetation anyway, therefore $f_\text{phen}$. Since the EMEP scheme is tuned to NH mid latitudes, the phenology does not apply to the tropics, hence, we later decided to set $f_\text{phen}$ to one if GLEN is greater or equal 365 which may be the case in the tropics and subtropics. The five phases described be the third case may dependent on surface type take a saddle or an trapezoidal shape (Fig.~\ref{fig:phenology}).

@@

  \caption{Scatch of the five different phases described in $f_\text{phen}$.}

@@

@@

  f_\text{light} = 1-\text{exp}(-\alpha_\text{light}\cdot \text{PPFD})

@@

@@

  g^\text{m}_{\text{max}} = g_{\text{max}} \cdot R \cdot \frac{T_\text{surf}}{P_\text{surf}}

@@

The non-stomatal conductance for \chem{O_3} consists of two terms, one depending on vegetation type and one depending in the soil/surface. For a land surface type $N$, we can write
\begin{equation}
  G_\text{ns}^\chem{O_3}(N) = \frac{\text{SAI}(N)}{r_\text{ext}} + \frac{1}{R_\text{inc}(N) + R_\text{gs}^\chem{O_3}(N)}.
\end{equation}
$\text{SAI}(N)$ is the surface area index for vegetation type $N$, which is $\text{LAI}$ plus some value representing cuticles and others surfaces. The external leaf resistance is defined by
\begin{equation}
  r_\text{ext} = 2000\cdot F_T\,\unit{sm^{-1}}.
\end{equation}
Herein $F_T$ is a temperature correction factor for temperatures below $-1\,\unit{^\circ C}$ and $\{F_T \in \mathbb{R} | (1 \leq F_T \leq 2)\}$
\begin{equation}
  F_T = \exp{(-2\cdot(1+\theta_0))}.
\end{equation}
$\theta_0$ is the surface or 2\,\unit{m} temperature in \unit{^\circ C}. In general, $\text{SAI} \equiv \text{LAI}$ for all land types, except for: 
%
\begin{equation}
  \text{SAI} = 
  \begin{cases}
    \text{LAI}+1 & \text{\emph{forest / wetland}},\\
    \text{LAI}\cdot 5/3.5 & \text{\emph{cropland}, I. part of growing season},\\
    \text{LAI} + 1.5 & \text{\emph{cropland}, II. part of growing season},\\
    0 & \text{\emph{cropland}, winter}.
  \end{cases}
\end{equation}
%
Extending the EMEP scheme to the southern hemisphere, the used growing season for crops is defined in Table~\ref{tab:growing_season}.
\begin{table}[t]
  \caption{Definition of growing season for crops used in the OsloCTM3 in northern hemisphere (NH) and southern hemisphere (SH).}
  \begin{tabular}{lrr}
    \tophline
    & I. part & II. part \\
    & (days) & (days) \\
    \middlehline
    NH & 90--140 & 141--270 \\
    SH & 272--322 & 323--452 \\
    \bottomhline
  \end{tabular}
  %\belowtable{} % Table Footnotes
  \label{tab:growing_season}
\end{table}
%

@@

\subsection{Dry deposition scheme for other gases and aerosols}
For \chem{NH_3}, \chem{SO_2}, and \chem{HNO_3}, we follow exactly the treatment as described by \citet{ACP:Simpson2012}. Since the dry deposition velocity for \chem{CO} is very small, we use a fixed value for $v_d^\chem{CO}$ of 0.03\,\unit{cms^{-1}}.

@@

    a_1 &  L \ge 0\,\unit{m}, \\
    a_1 \cdot F_N \left[ 1 + \left(\frac{a_2}{25}\right)^{2/3}\right]& -25\,\unit{m} < L < 0\,\unit{m}, \\
    a_1 \cdot F_N \left[ 1 + \left(\frac{-a_2}{L}\right)^{2/3}\right]& L \le -25\,\unit{m}, \\

@@

  a_1^\text{hydrophob.} = 0.025\,\unit{cms^{-1}} \cdot \overline{u_*}

@@

  a_1^\text{hydrophil.} = 0.2\,\unit{cms^{-1}} \cdot \overline{u_*},

@@

    \emph{land} &

@@

      \emph{non-forest} &  a_1^\text{hydrophob.}\\
      \emph{forest} &

@@

        \emph{dry} & \max{(a_1^\text{hydrophob.}, 0.008\cdot\frac{\text{SAI}}{10})}\\
        \emph{wet} & 1.5\cdot\max{(a_1^\text{hydrophob.}, 0.008\cdot\frac{\text{SAI}}{10})}\\

@@

    \emph{ocean} &

@@

    \emph{ice} &

@@

      \theta \le 0\,\unit{^\circ C} & a_1^\text{hydrophob.}\\
      \theta > 0\,\unit{^\circ C} &

@@

As mentioned in the previous section, there are two variables needed for computing the stomatal conductance which are not directly available from the meteorological input data. The greening season, as the time of the year in the mid and high latitudes when it is most likely for plants to grow, and the photosynthetic photon flux density, as the varying amount of light plants can use to photosynthesize.

@@

The EMEP scheme is making extensive use of the time elapsed since the onset of the greening season and the total length of the greening season. There is a latitude dependent parameterization for the greening season that may work well for all but high northern latitudes, especially in Europe, and is not taking meteorology into account.  
\subsubsection{Photosynthetic photon flux density (PPFD)}
From OpenIFS an accumulated photoactive radiation (PAR) is available, but needs to be deaccumulated. Strictly speaking, since this field is already integrated over the whole spectrum, it is not the actual PAR but PPFD. 
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_{ice/snow} = 1/10000\,\unit{cm s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...
\section{Discussion}
\label{sec:disc}

>>>>

The aerodynamic resistance is describing the turbulent transport of any substance down to the surface. In \citet{WASP:Simpson2003,ACP:Simpson2012} it is described as

@@

Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}

@@

Over ocean, we use \citep[Eq.~(54),][]{ACP:Simpson2012}

@@

For the temperature dependent dynamic viscosity of air $\mu(T)$, we chose a linear fit to Sutherland's law through the origin within the temperature range $\{T \in \mathbb{R} | (243.15 < T < 313.15)\,\unit{K}\}$: $\mu(T) = 6.2\cdot 10^{-8}\,\unit{kg \, m^{-1} s^{-1} K^{-1}} \cdot T$. But despite its rough accuracy, we found that the choice of $\mu(T)$ has no effect on $\left<R_b\right>$ (Supplement S.1). In Eq.~(\ref{eq:kinematic_viscosity}), $\rho$ is substituted by the air density using the ideal gas law. $P_0$ is the surface pressure, as $T$ the 2\,\unit{m} temperature is chosen, and $R_\text{air}$ is the universal gas constant for air.

@@

  G_c = \text{LAI} \cdot G_\text{sto} + G_\text{ns}, 

@@

wherein $\text{LAI}$ is the leaf area index (zero for non-vegetated surfaces), $G_\text{sto}$ the stomatal conductance, and $G_\text{ns}$ the non-stomatal conductance.

@@

The stomatal conductance is a measure of the rate of \chem{CO_2} entering or evapotranspiration through the stomata of a leaf. There are several environmental conditions affecting the opening and closing of the stomata and hence their capability of respiration (e.g., light, available water, etc.). Stomata sluggishness, a state in which the stomata can no longer fully close, has been reported as ozone induced damage \citep{SR:Hoshika2015}. To reflect part of the underlying mechanism, the stomatal conductance $g_\text{STO}$ in the EMAP scheme is computed using a multiplicative ansatz that is also explained in much detail in \citet{ICP:MappingManual2017}:

@@

  \label{eq:stomatal}

@@

with $\beta = \frac{T_\text{max}-T_\text{opt}}{T_\text{opt}-T_\text{min}}$. The parameters $T_\text{min}$, $T_\text{max}$ and $T_\text{opt}$ are tabulated for various land surface types. All parameters used in the EMEP scheme can be found in the supplementary to \citet{ACP:Simpson2012} or in Supplement~S.2. Since $f_\text{T}$ becomes negative outside its range defined by $T_\text{min}$, $T_\text{max}$, we impose a lower limit of $0.01$. The water vapor deficit (VPD) is proportional to the saturation partial pressure of water ($P_\chem{H_2O}^s$) and relative humidity ($\text{RH}$)

@@

Using tabulated values of $f_\text{min}$, $D_\text{min}$, $D_\text{max}$, the water vapor pressure deficit penalty factor can be computed:

@@

The penalty factor with respect to available soil water ($\text{SW}$) is defined as 

@@

    1 & \quad \emph{if} \quad \text{SW} \geq 0.5,\\
    2 \cdot \text{SW}  & \quad \emph{if} \quad \text{SW} < 0.5.

@@

\citet{ACP:Simpson2012} suggest using SW in soil depths below 1\,\unit{m} (SWVL4 in OpenIFS). Throughout most of our simulations (Section~\ref{sec:eval}), we have, however, used the soil water contained in the top layer (SWVL1, $0-7\,\unit{cm}$), which makes the canopy conductance much more sensitive to precipitation than it would be otherwise. The phenology of a plant typically describes its lifecycle through out a year, e.g., in mid latitudes and for deciduous species, it starts with the emergence of leafs in spring and ends in fall. In the EMEP scheme, phenology is parameterized with respect to the begin of the greening season (GDAY) and its length (GLEN). Details about our choice of GDAY and GLEN are given in Section~\ref{subsubsec:greening}. In summary, the $f_\text{phen}$ parameterization reads as follows:

@@

    \emph{if} \quad \text{GDAY = 0}  & \quad 0 \\
    \emph{if} \quad \text{GLEN $\ge$ 365} & \quad 1 \quad \emph{(explicitly excluding Tropics)} \\

@@

      \emph{if} \quad \text{GDAY} \le \phi_\text{AS}  & \quad \phi_a \\
      \emph{if} \quad \text{GDAY} \le \phi_\text{AS} + \phi_e  & \quad \phi_b+(\phi_c-\phi_b)\cdot(\text{GDAY}-\phi_\text{AS})/\phi_e\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE} - \phi_f  & \quad \phi_c\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE}  & \quad \phi_d+(\phi_c-\phi_d)\cdot(\text{GLEN}-\phi_\text{AE}-\text{GDAY})/\phi_f\\

@@

The parameters $\phi_a$, $\phi_b$, $\phi_c$, and $\phi_d$ define start or end points in the five phases of phenology in the EMEP scheme, while $\phi_e$, $\phi_f$, $\phi_\text{AS}$, and $\phi_\text{AE}$ control the temporal timing (Fig.~\ref{fig:phenology}). If GDAY is zero we are most likely in Arctic regions and there is no vegetation anyway, therefore $f_\text{phen}=0$. Since the EMEP scheme is tuned to NH mid latitudes, this phenology does not apply to the tropics, after evaluation of the model results (Section~\ref{subsec:sens}), we decided to set $f_\text{phen}=1$ if GLEN is greater or equal 365 which is the case in the tropics.

@@

  \caption{Sketch of the five different phases described in $f_\text{phen}$.}

@@

Light in the wavelength band $(400-700)$\,\unit{nm} to which the plant chlorophyll is sensitive is called photosynthetic active radiation (PAR). In the EMEP parameterization, an integrated photon flux -- photosynthetic photon flux density (PPFD) -- is used to mimic the time lag of the opening and closing of stomata with respect to light instead of a simple day-on/night-off treatment:

@@

  f_\text{light} = 1-\text{exp}(-\alpha_\text{light}\cdot \text{PPFD}).

@@

Since $g_\text{max}$ in Eq.~(\ref{eq:stomatal}) is in units of \unit{mmol\,s^{-1}\,\,m^{-2}}, a unit conversion is done:

@@

  g^\text{m}_{\text{sto}}(N) = g_{\text{sto}}(N) \cdot R \cdot \frac{T_0}{P_0}.
Herein $R$ is the universal gas constant. With this the total gridbox stomatal conductance $G_\text{sto}$ is computed weighted by the land surface type fraction $f_L(N)$:
  G_\text{sto} = \sum_{N=0}^{N_\text{max}} f_L(N)\cdot g^\text{m}_{\text{sto}}(N)

@@

The non-stomatal conductance for \chem{O_3} consists of two terms, one depending on vegetation type and one depending in the soil/surface. For a land surface type $N$, we can write
\begin{equation}
  G_\text{ns}^\chem{O_3}(N) = \frac{\text{SAI}(N)}{r_\text{ext}} + \frac{1}{R_\text{inc}(N) + R_\text{gs}^\chem{O_3}(N)}.
\end{equation}
$\text{SAI}(N)$ is the surface area index for vegetation type $N$, which is $\text{LAI}$ plus some value representing cuticles and others surfaces. The external leaf resistance is defined by
\begin{equation}
  r_\text{ext} = 2000\cdot F_T\,\unit{sm^{-1}}.
\end{equation}
Herein $F_T$ is a temperature correction factor for temperatures below $-1\,\unit{^\circ C}$ and $\{F_T \in \mathbb{R} | (1 \leq F_T \leq 2)\}$
\begin{equation}
  F_T = \exp{(-2\cdot(1+\theta_0))}.
\end{equation}
$\theta_0$ is the surface or 2\,\unit{m} temperature in \unit{^\circ C}. In general, $\text{SAI} \equiv \text{LAI}$ for all land types, except for: 
%
\begin{equation}
  \text{SAI} = 
  \begin{cases}
    \text{LAI}+1 & \emph{if} \quad \text{\emph{forest / wetland}},\\
    \text{LAI}\cdot 5/3.5 & \emph{if} \quad \text{\emph{cropland}, I. part of growing season},\\
    \text{LAI} + 1.5 & \emph{if} \quad \text{\emph{cropland}, II. part of growing season},\\
    0 & \emph{if} \quad \text{\emph{cropland}, winter}.
  \end{cases}
\end{equation}
%
Extending the EMEP scheme to the southern hemisphere, the used growing season for crops is defined in Table~\ref{tab:growing_season}.
\begin{table}[t]
  \caption{Definition of growing season for crops used in the OsloCTM3 in northern hemisphere (NH) and southern hemisphere (SH).}
  \begin{tabular}{lrr}
    \tophline
    & I. part & II. part \\
    & (days) & (days) \\
    \middlehline
    NH & 90--140 & 141--270 \\
    SH & 272--322 & 323--452 \\
    \bottomhline
  \end{tabular}
  %\belowtable{} % Table Footnotes
  \label{tab:growing_season}
\end{table}
%

@@

\subsection{Dry deposition scheme for other gases and aerosols}
For \chem{NH_3}, \chem{SO_2}, and \chem{HNO_3}, we follow exactly the treatment as described by \citet{ACP:Simpson2012}. Since the dry deposition velocity for \chem{CO} is very small, we use a fixed value for $v_d^\chem{CO}$ of 0.03\,\unit{cm\,s^{-1}}.

@@

    a_1 &  \emph{if} \quad L \ge 0\,\unit{m}, \\
    a_1 \cdot F_N \left[ 1 + \left(\frac{a_2}{25}\right)^{2/3}\right] & \emph{if} \quad -25\,\unit{m} < L < 0\,\unit{m}, \\
    a_1 \cdot F_N \left[ 1 + \left(\frac{-a_2}{L}\right)^{2/3}\right] & \emph{if} \quad L \le -25\,\unit{m}, \\

@@

  a_1^\text{hydrophob.} = 0.025\,\unit{cm\,s^{-1}} \cdot \overline{u_*}

@@

  a_1^\text{hydrophil.} = 0.2\,\unit{cm\,s^{-1}} \cdot \overline{u_*},

@@

    \emph{if} \quad \emph{land} &

@@

      \emph{if} \quad \emph{non-forest} &  a_1^\text{hydrophob.}\\
      \emph{if} \quad \emph{forest} &

@@

        \emph{if} \quad \emph{dry} & \max{(a_1^\text{hydrophob.}, 0.008\cdot\frac{\text{SAI}}{10})}\\
        \emph{if} \quad \emph{wet} & 1.5\cdot\max{(a_1^\text{hydrophob.}, 0.008\cdot\frac{\text{SAI}}{10})}\\

@@

    \emph{if} \quad \emph{ocean} &

@@

    \emph{if} \quad \emph{ice} &

@@

      \emph{if} \quad \theta \le 0\,\unit{^\circ C} & a_1^\text{hydrophob.}\\
      \emph{if} \quad \theta > 0\,\unit{^\circ C} &

@@

As mentioned in the previous section, there are two variables needed for computing the stomatal conductance which are not directly available from the meteorological input data. The greening season, as the time of the year in the mid and high latitudes when it is most likely for plants to grow, and the photosynthetic photon flux density, as the amount of light plants need to photosynthesize. In the following, we present the necessary pre-processing of the variables.

@@

The original EMEP scheme uses fixed start of growing season (SGS) and end of growing season (EGS) at $50\,\unit{^\circ N}$ together with leapsrates ($d_\text{SGS}$, $d_\text{EGS}$, $\nabla d_\text{SGS}$, and $\nabla d_\text{EGS}$ in Supplement~S.2) to define phenology and dry deposition over agricultural areas. However this parameterization fails in a global model, therefor another latitude dependent parameterization is needed. First, we have used a parameterization as implemented in the Sparse Matrix Operational Kernel Emissions -- Biogenic Emission Inventory System (SMOKE-BEIS) model. SMOKE-BEIS has fixed values for SGS and EGS for all regions but NH mid latitudes ($23\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$), where it uses leapsrates of $\nabla d_\text{SGS} = 4.5$ and $\nabla d_\text{EGS} = 3.3$. This parameterization works well, if the focus of the scientific work lies on mid latitudes and North America. In Europe, however, most of northern Scandinavia has no vegetation period according to this parameterization.

In agriculture, there are differing empirical rules to estimate the SGS and EGS. The simplest assumption is that greening starts after 5 consecutive days with a daily average temperature above 5\,\unit{^\circ C} and vice versa for EGS. If, within these 5 days, the temperature drops below / rises above 5\,\unit{^\circ C}, the counters are reset. With respect to model performance, we decided to preprocess our meteorological input date using this 5\,\unit{^\circ C}-days criteria for $45\,\unit{^\circ} < \text{lat} < 85\,\unit{^\circ}$ in the NH and $35\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$ in the SH. In all other cases and where the 5\,\unit{^\circ C}-days criterion fails, we use the SMOKE-BEIS parameterization.

Instead of SGS and EGS, we use the derived parameters day of greening season (GDAY), which is the time elapsed starting at the SGS, and the total length of the greening season (GLEN), which is the time between EGS and SGS. Example maps of the computed GLEN are shown in Supplement~S.4.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photosynthetic photon flux density (PPFD)}
From OpenIFS an accumulated photosynthetic active radiation (PAR) is available, but needs to be deaccumulated. Strictly speaking, since this field is already integrated over the whole spectrum, it is not the actual PAR but PPFD. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:disc}
